\documentclass[twocolumn]{aastex62}


\newcommand\x         {\hbox{$\times$}}
\newcommand\othername {\hbox{$\dots$}}
\def\eq#1{\begin{equation} #1 \end{equation}}
\def\eqarray#1{\begin{eqnarray} #1 \end{eqnarray}}
\def\eqarraylet#1{\begin{mathletters}\begin{eqnarray} #1
                  \end{eqnarray}\end{mathletters}}
\def\mic              {\hbox{$\mu\mathrm{m}$}}
\def\about            {\hbox{$\sim$}}
\def\Mo               {\hbox{$M_{\odot}$}}
\def\Lo               {\hbox{$L_{\odot}$}}
\def\comm#1           {\texttt{(COMMENT: #1)}}
\def\kms   {\hbox{km s$^{-1}$}}

\usepackage{graphicx}
\usepackage{xspace}

\newcommand{\B}[1]{{#1}}

\shorttitle{The Large Synoptic Survey Telescope}
\shortauthors{Ivezi\'{c}, Tyson, Abel, Acosta, Allsman, Alonso, AlSayyad, Anderson, Andrew, et al.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{LSST: from Science Drivers to Reference Design and Anticipated Data Products}

\AuthorCallLimit=999
\include{authors}
\include{abstract}

\input{introduction}
\input{system}
\input{dataproducts}
\input{science}
\input{community}
\input{epo}
\input{conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\acknowledgments
In 2003, the LSST Corporation was formed as a non-profit 501(c)3 Arizona corporation
with headquarters in Tucson, AZ.  Membership has since expanded to
more than forty institutional members
including Adler Planetarium, Argonne National Laboratory, Brookhaven National Laboratory, California Institute of Technology,
Carnegie Mellon University, Chile,  Columbia University, Cornell University, Drexel University,
Fermi National Accelerator Laboratory, George Mason University, Google Inc., Harvard-Smithsonian
Center for Astrophysics, Institut de Physique Nucl\'eaire et de Physique des Particules, Johns Hopkins
University, Kavli Institute for Particle Astrophysics and Cosmology -- Stanford University, Las
Cumbres Observatory Global Telescope Network, Inc., Lawrence Livermore National Laboratory,
Los Alamos National Laboratory,  National Optical Astronomy
Observatory, National Radio Astronomy Observatory, Northwestern
University, Oxford University,
Princeton University, Purdue University, Research Corporation for Science Advancement, Rutgers
University, SLAC National Accelerator Laboratory, Space Telescope Science Institute,
Texas A\&M University, The Pennsylvania State University, The University of Arizona, University
of California at Davis, University of California at Irvine, University College London, University of
Illinois at Urbana-Champaign, University of Michigan, University of Pennsylvania, University of
Pittsburgh, University of Washington, and Vanderbilt and Fisk Universities.

LSST is a public-private partnership.  Design and development activity is
supported by in part the National Science Foundation under Scientific
Program Order No.~9 (AST-0551161), Scientific Program Order No.~1
(AST-0244680) through Cooperative Agreement AST-0132798, and grant AST-0441069.
Portions of this work are supported by the Department of Energy under contract
DE-AC02-76SF00515 with the Stanford Linear Accelerator Center, contract
DE-AC02-98CH10886 with Brookhaven National Laboratory, contract
DE-AC52-07NA27344 with Lawrence Livermore National Laboratory, and grants
DE-FG02-07ER41505 and DE-SC0007881. A portion of this work was conducted at the Jet Propulsion
Laboratory, California Institute of Technology, under a contract with NASA.
Gifts by the Charles Simonyi Fund for Arts and Sciences,
and Bill Gates, and grants by W. M. Keck Foundation and the TABASGO Foundation
are gratefully acknowledged. Additional funding has been provided by private gifts, grants
to universities, and in-kind support at Department of Energy laboratories and other
LSSTC Institutional Members.

NOAO is operated by the Association of Universities for Research in Astronomy,
Inc.\ (AURA) under cooperative agreement with the National Science Foundation.

This work was supported in part by National Science Foundation Grant No. PHYS-1066293
and the hospitality of the Aspen Center for Physics.

We thank Chris Borden, Tim Knauer and Branimir Sesar for valuable comments.

\facility{LSST}

\appendix

\section{Version History}

\vskip 0.06in
Version 1.0 (May 15, 2008): the first posting.
\vskip 0.06in
Version 2.0 (June 7, 2011): acknowledged the Decadal Survey 2010 report; updated construction schedule;
updated expected performance in Table 2; added sections on LSST simulations and data mining;
updated several figures; updated references; expanded author list.
\vskip 0.06in
Version 3.0 (August 26, 2014): acknowledged the start of federal construction;
updated system description and science examples, updated several figures; refreshed references;
expanded author list.
\vskip 0.06in
Version 4.0 (February 28, 2018): updated system description and science examples, updated expected
performance in Table 2; updated several figures; refreshed references; expanded author list.

\bibliography{lsst}
%\allauthors

\end{document}




% latex lsst; dvips -Ppdf -o lsst.ps lsst.dvi; ps2pdf14 lsst.ps lsst.pdf
